Representation Learning for Generalized Planning - SAT Encodings

### 2020-09-03 doc/encodings/paper.tex
Update encoding description with goal-distinguish constraints
Reorganize blocks experiments

\documentclass[a4paper]{article}
%\def\year{2020}\relax
%\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS

@@

\noindent where $Dist(s, s', t, t')$ is shorthand for $\bigvee_{f \in D2(s, s', t, t')} Select(f)$.

@@

@@

>>>>

\documentclass[a4paper]{article}
%\def\year{2020}\relax
%\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
%\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
%\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS

\usepackage[margin=1in]{geometry}

@@

\noindent where $Dist(s, s', t, t')$ is shorthand for $\bigvee_{f \in D1\&2(s, s', t, t')} Select(f)$.

@@

\smallpar{C11}
Goals can be distinguished from non-goals.
\begin{align}
\bigvee_{f \in D1(s, s')} Select(f),&\;\; \text{for $s$ goal, $s$ not a goal}
\end{align}

@@

\section{Empirical Results}

\subsection{Blocks:clear}
Two instances of 5 blocks.
1 iteration, 19759 vars + 69255 clauses
Number of transitions/equivalence classes: 1161/55
Optimal MAXSAT solution with cost 5 found

\begin{verbatim}
0. n(a) DECs AND n-ontable NILs AND n-ontable>0
1. n(a) NILs AND n-ontable INCs AND n-ontable>0
\end{verbatim}

\subsection{Blocks:on}
\begin{verbatim}
0. clear(a) ADDs AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) NILs
1. clear(a) DELs AND holding(·) ADDs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)=0
2. clear(a) NILs AND clear(a)=0 AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
3. clear(a) ADDs AND holding(·) DELs AND n-single-blocks NILs AND not-clear(b) ADDs
4. clear(a) ADDs AND holding(·) DELs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)>0
5. clear(a) NILs AND clear(a)>0 AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs AND not-clear(b)>0
6. clear(a) DELs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
7. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)>0
8. clear(a) NILs AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks=0 AND not-clear(b) NILs AND not-clear(b)=0
9. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs
10. clear(a) ADDs AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)>0
11. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) NILs
12. clear(a) ADDs AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) ADDs
13. clear(a) DELs AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)=0
14. clear(a) NILs AND clear(a)=0 AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) DELs
15. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) NILs AND not-clear(b)=0
16. clear(a) NILs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) DELs
17. clear(a) NILs AND clear(a)>0 AND holding(·) ADDs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) DELs
18. clear(a) ADDs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
19. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks=0 AND not-clear(b) NILs AND not-clear(b)>0
20. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)>0
\end{verbatim}
